KeysarMouseTracking.csv

### 2016-01-21 experiment2/analysis/exp2Analysis.Rmd
Fix number of participants to include in denominator

```{r}
nonNativeEnglishIDs <- c("0366-3", "8676-f")
numParticipants <- length(unique(mouseD$gameid))
nonCriticalMistakes <- errorD %>%
  # only look at mistakes on noncritical (filler) items
  filter(critical != 1) %>%
  # don't want to double-count people for messing the same thing up multiple times
  filter(attemptNum == 0) %>% 
  group_by(gameid) %>%
  tally() %>%
  # implement exclusion criteria of errors on >~10% of non-critical trials
  filter(n >= 2)

mistakeIDs <- as.character(nonCriticalMistakes$gameid)
bannedIDs <- c(mistakeIDs, nonNativeEnglishIDs)
```

@@

```{r}
eD <- errorD %>%
  filter(!(gameid %in% mistakeIDs)) %>%
  filter(!(gameid %in% nonNativeEnglishIDs)) %>%
  filter(critical == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  tally() %>%
  mutate(cond2 = as.numeric(n >= 2)) %>%
  group_by(condition) %>%
  summarise(atLeastOnce = length(n)/numParticipants, 
            atLeastTwice = sum(cond2)/numParticipants,
            total = sum(n) / (4 * numParticipants))
eD

# To illustrate how much a few items are driving the effect, we exclude three items 
# where more than 60% of participants made errors.
excludedED <- errorD %>%
  filter(!(gameid %in% bannedIDs)) %>%
  filter(critical == 1) %>%
  filter(!(objectSet %in% c(5, 6, 8))) %>% # Just 5 & 6?
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  tally() %>%
  mutate(cond2 = as.numeric(n >= 2)) %>%
  group_by(condition) %>%
  summarise(atLeastOnce = length(n)/numParticipants, 
            atLeastTwice = sum(cond2)/numParticipants,
            total = sum(n) / (4 * numParticipants))
excludedED
```

>>>>

```{r}
nonNativeEnglishIDs <- c("0366-3", "8676-f")
nonCriticalMistakes <- errorD %>%
  # only look at mistakes on noncritical (filler) items
  filter(critical != 1) %>%
  # don't want to double-count people for messing the same thing up multiple times
  filter(attemptNum == 0) %>% 
  group_by(gameid) %>%
  tally() %>%
  # implement exclusion criteria of errors on >~10% of non-critical trials
  filter(n >= 2)

mistakeIDs <- as.character(nonCriticalMistakes$gameid)
bannedIDs <- unique(c(mistakeIDs, nonNativeEnglishIDs))
numParticipants <- length(unique(mouseD$gameid)) - length(bannedIDs)
```

@@

```{r}
eD <- errorD %>%
  filter(!(gameid %in% bannedIDs)) %>%
  filter(critical == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  tally() %>%
  mutate(cond2 = as.numeric(n >= 2)) %>%
  group_by(condition) %>%
  summarise(atLeastOnce = length(n)/numParticipants, 
            atLeastTwice = sum(cond2)/numParticipants,
            total = sum(n) / (4 * numParticipants))
eD

# To illustrate how much a few items are driving the effect, we exclude three items 
# where more than 60% of participants made errors.
excludedED <- errorD %>%
  filter(!(gameid %in% bannedIDs)) %>%
  filter(critical == 1) %>%
  filter(!(objectSet %in% c(5, 6))) %>% # Just 5 & 6?
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  tally() %>%
  mutate(cond2 = as.numeric(n >= 2)) %>%
  group_by(condition) %>%
  summarise(atLeastOnce = length(n)/numParticipants, 
            atLeastTwice = sum(cond2)/numParticipants,
            total = sum(n) / (4 * numParticipants))
excludedED
```
